\section*{Preface}
These notes serve as a single source of knowledge in which those reading should ideally be able to garner a deeper understanding of the thoughts and ideas about piecewise objects I have had and continue to have.

If you have trouble understanding some of the ideas presented here, you should consider taking a look at the blog posts on \url{https://piecewise.org} or contacting myself at ally@piecewise.org. The things you'll see here are the culmination of many hundreds of hours scribbling, doodling and refining thoughts over the course of several years. More importantly than the fact I am myself still learning the fundamentals of mathematics at a higher level, is that you understand that trial and lots of error forms the majority of this work.

With this being said, there is the distinct possibility that these notes are the culmination of wasted effort and crackpotery :-). It's entirely possible people have stumbled on these same or similar ideas, simply notated differently, as is prevalent in all undergraduate students learning new (old) maths, including myself.

Thank you in advance for reading.

\section{Introduction}
To consider something piecewise is to enumerate something under differing conditions. For example, one might consider the function $\abs{x}$ piecewise, namely $\abs{x}=x$ when $x\geq 0$ or $\abs{x}=-x$ when $x\leq 0$.

An object which is piecewise is something which contains a set of pieces, which themselves contain values and conditions, under which those values are taken for the overall object. Continuing with the example of $\abs{x}$, we have the piece value $x$ for when $x\geq 0$, the condition, (which forms a piece), and $-x$ for when $x\leq 0$.

We shall develop ideas such as above more explicitly throughout these notes. These ideas often intersect with other areas of maths, which one might be familiar with --- but if not, don't panic; such ideas are not strictly foundational to the presented notes.

Furthermore, these notes focus on construction; rather than evaluating existing concepts or formulas, we focus on deriving existing or new tools, ideas and formulas. For you, reader, this must be a process you should become familiar with, and rather than just reading these notes, attempt to follow along by hand, and construct your own objects using the ideas presented here. We also stress that with ideas that intersect with more mainstream mathematics, that existing concepts be used to evaluate the validity of the constructions. Moreover, we attempt to make these ideas and tools systematic when applied to piecewise functions, so as to develop algorithms and consistently draw parallels to existing methods (for example, we may derive a formula which can then be verified by induction).

As to a preview of what's to come: we develop ideas and formulations for elementary function based formulations of typically piecewise-denoted functions, do some probably piecewise algebra, interpolate points and other functions, construct squares, shapes, re-develop the batman equation but continuously, paint some graphs, think about what happens when we mix in complex numbers, and more.


\newpage